A pipeline to analyse time-course gene expression data

### 2019-08-30 scripts/manuscript.Rmd
ENH added a note about count versus microarray data
More information in supplementary

**EAP: We need to add comment about microarray versus sequencing data**

@@

@@

go_terms_enriched = go_terms_enriched[
    order(go_terms_enriched[, "resultFisher_padj"]), ]
colnames(go_terms_enriched) = c("GO ID", "Description", "Annotated",
"Significant", "Expected", "P-value", "adj. p-value")

kable(go_terms_enriched[1:15, ], format="latex", escape=F, digits=4, booktabs=TRUE)
```

# Session information

>>>>

@@

While we showcase this pipeline on micro-array data, [@varoquaux:lifecycle]
leverages a similar set of steps to analyse RNA-seq data of the lifetime
transcriptomic response of the crop *S. bicolor* to drought.

@@

go_terms_enriched = go_terms_enriched[
    order(go_terms_enriched[, "resultFisher_padj"]), ]
colnames(go_terms_enriched) = c("GO ID", "Description", "Annotated",
"Significant", "Expected", "P-value", "Adj. p-value")

kable(go_terms_enriched[1:15, ], format="latex", escape=F,
      digits=3, booktabs=TRUE, row.names=FALSE)
```

The source code for this workflow can be found at
[https://github.com/NelleV/2019timecourse-rnaseq-pipeline](https://github.com/NelleV/2019timecourse-rnaseq-pipeline).
Archived source code at the time of publication can be foud at [XXX](XXX).

All packages use in the workflow are available on GitHub, CRAN, or
Bioconductor.

Data used in this workflow are available from NCBI GEO, accession
[GSE63786](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE63786).
Normalized data can be found in `moanin`.  Normalization information is
provided as supplementary information.

Last but not least, we use `sessionInfo()` to display all packages used in
this pipeline and their version numbers.
